\documentclass{article}

\usepackage{fullpage}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{color}
\usepackage{calligra}
\usepackage[T1]{fontenc}
\usepackage{wesa}
\usepackage[T1]{fontenc}
\usepackage{pbsi}
\usepackage[T1]{fontenc}


\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{(\alph{enumii})}

\begin{document}

\begin{center}{\Large\textbf{CSCC01 Team Expectation Agreement}}\end{center}
\begin{center}{\large{\textbf{Group: UofToilets}}}\end{center}

\section{Contractual Obligations}
    \subsection{Meetings}
        As a team we agree to the following conditions surrounding the scheduling and conduct of meetings:
        \begin{enumerate}
            \item Meetings will be held twice weekly, on Monday at 8:00pm via the course discord server, and Wednesday at 2:00pm following the tutorial as a hybrid model.
            \item Changes in attendance will be communicated to the group 24 hours in advance of the scheduled meeting time. Emergency situations will be considered.
            \item Conduct within the meetings will be professional and respectful towards all group members.
            \item Members will be prepared to share progress and raise concerns or difficulties with the rest of the group. If a member is unable to attend a meeting they will inform the group of their progress via the text channel.
            \item Meeting minutes will be recorded and will be shared with members as requested.
        \end{enumerate}
    \subsection{Communication Methods}
        As a team we agree to the following terms and conditions surrounding communication:
        \begin{enumerate}
            \item The main method of communication will be the provided discord server, verbal communication will be conducted both in person and through the provided voice channel.
            \item Members are expected to respond to messages within 24 hours of the message being sent.
            \item When communicating with members of the group, conduct is expected to remain professional and respectful towards all group members.
        \end{enumerate}
    \subsection{Contingency Plans}
        If there are changes to plans regarding communications or meetings, the following terms and conditions will apply:
        \begin{enumerate}
            \item A change in time or location must be communicated to the group 6 hours in advance of the scheduled meeting time.
            \item A meeting may be cancelled if the desire to do so is communicated to the group 6 hours in advance of the scheduled meeting time.
            \item In order to cancel a meeting a majority vote must occur, and it must be the desire of said majority to cancel the meeting in order to proceed.
            \item A member may miss up to a maximum of two meetings, unless...
                \begin{enumerate}
                    \item A medical or family emergency has occurred.
                    \item Other extenuating circumstances, requiring prior approval from one or more group members and a notification to the Scrum Master.
                \end{enumerate}
        \end{enumerate}
    \subsection{Breach of Agreement}
        A member who fails to meet the above specified requirements will be considered under breach of agreement unless excused by the rest of the group. It is up to the discretion of group members to determine which instances require proof for certain excuses. If any conflict arises the TA/Professor will be notified.
        
\section{Consequences for Breach of Agreement}
    This section specifies the procedures and punishments associated with deviation from terms outlined in the 'Contractual Obligations Section'
    \begin{enumerate}
        \item \textbf{It is agreed that if a group member is in breach of this team agreement the following actions will be taken...}
            \begin{enumerate}
                \item A written warning will be sent via discord messaging, as well as email to the individual outlining the complaint, providing evidence and supporting documents relating to the identified issue. The TA and professor will be copied on this correspondence.
            \end{enumerate}
        \item \textbf{It is agreed that as an individual, if the failure to meet the agreed upon conditions falls upon myself...}\
            \begin{enumerate}
                \item The individual will respond in writing, via both discord and email to the provided warning and a detailed plan including a timeline will be provided identifying steps that will be taken to remedy the issue. The TA and professor will be copied on this correspondence.
            \end{enumerate}
        \item \textbf{It is agreed that if the same or similar problem occurs more than once, or if the identified issue resolves unresolved...}
            \begin{enumerate}
                \item The professor will be contacted detailing the intention to 'fire' or report a team member (via email, discord, etc.) that states the reason for the issue and provides evidence for the described problem.
                \item In the event that a team member is fired from the team they will be responsible for completing the rest of the project on their own, and their name and credentials will no longer be attached to future team submissions.
            \end{enumerate}
    \end{enumerate}

\newpage
\section{Signatures}
In appending your signature below you are stating that,
\begin{enumerate}
    \item You participated in formulating the standards, roles, and procedures of this Agreement.
    \item You have agreed to abide by these terms and conditions of this Agreement.
    \item You understand that you will be subject to the consequences specified above and may be subject to reduction in overall course grade (including a failing grade) in the event that you do not fulfil the terms of this agreement.
\end{enumerate}

\centering{\textbf{Printed Name (UtorId)} \hspace{2cm} \textbf{Signature} \hspace{4cm} \textbf{Date}}
\newline
\newline
\begin{center}
    \underline{Sebastian Jingoi (jingoise)\hspace{0.8cm}}\hspace{1.5cm}\underline{\calligra{Sebastian Jingoi}\hspace{1.7cm}}\hspace{1.5cm} \underline{2024-02-11\hspace{1.25cm}} \newline
\end{center}
\begin{center}
    \underline{Zain Rizvi (rizviza7)\hspace{1.8cm}}\hspace{1.5cm}{\underline{\bsifamily{Zain Rizvi}\hspace{2.3cm}}}\hspace{1.4cm} \underline{2024-02-11\hspace{1.25cm}} \newline
\end{center}
\begin{center}
    \underline{Kieran Hansen (hansen20)\hspace{1cm}}\hspace{1.5cm}\underline{\calligra{Kieran Hansen}\hspace{1.7cm}}\hspace{1.5cm} \underline{2024-02-11\hspace{1.25cm}} \newline
\end{center}
\begin{center}
    \underline{\hspace{5cm}}\hspace{1.5cm}\underline{\hspace{4cm}}\hspace{1.5cm} \underline{\hspace{3cm}} \newline
\end{center}
\begin{center}
    \underline{\hspace{5cm}}\hspace{1.5cm}\underline{\hspace{4cm}}\hspace{1.5cm} \underline{\hspace{3cm}} \newline
\end{center}
\begin{center}
    \underline{\hspace{5cm}}\hspace{1.5cm}\underline{\hspace{4cm}}\hspace{1.5cm} \underline{\hspace{3cm}} \newline
\end{center}
\end{document}
